Simulations

### 2020-12-09 Simulations.Rmd
Update Simulations.Rmd

```{r}
# Read in and filter data
data <- read_csv("Data/game.csv")
data <- data %>% filter(data$season == 20132014, data$home_team_id %in% c(seq(1,30), 52), data$away_team_id %in% c(seq(1,30), 52), data$type == 'R')
data$home_team_id[data$home_team_id == 52] <- 11
data$away_team_id[data$away_team_id == 52] <- 11
```

@@

# Calculate tie threshhold.
alpha <- qnorm(0.612, 0, sqrt(2 * (tao^2 + sigma^2)))
```

@@

  # Go through and calculate outcomes
  for (game in 1:length(games[[1]])) {
    # If there is a tie award 2 points to the 'winner'
    if (abs(games[[6]][game]) >= alpha) {
      if (games[[6]][game] >= 0) {
        games[[7]][game] <- 2
      }
      else {
        games[[8]][game] <- 2
      }
    }
    # Else rescale performances and simulate a winner, giving two points to the winner and one to the loser
    else {
      zeta <- (games[[6]][game] - a) / b
      if (rbernoulli(1, p = zeta)) {
        games[[7]][game] <- 2
        games[[8]][game] <- 1
      }
      else {
        games[[7]][game] <- 1
        games[[8]][game] <- 2
      }
    }
  }

>>>>

# Read and filter the data
```{r}
data <- read_csv("Data/game.csv")
data <- data %>% filter(data$season == 20132014, data$home_team_id %in% c(seq(1,30), 52), data$away_team_id %in% c(seq(1,30), 52), data$type == 'R')
data$home_team_id[data$home_team_id == 52] <- 11
data$away_team_id[data$away_team_id == 52] <- 11
```

@@

# Calculate tie threshhold.
alpha <- qnorm(0.612, 0, sqrt(2 * (tao^2 + sigma^2)))

```

@@

  # Go through and calculate outcomes
  for (game in 1:length(games[[1]])) {
    # If there is a tie award 2 points to the 'winner'
    if (abs(games[[6]][game]) >= alpha) {
      if (games[[6]][game] >= 0) {
        games[[7]][game] <- 2
      }
      else {
        games[[8]][game] <- 2
      }
    }
    # Else rescale performances and simulate a winner, giving two points to the winner and one to the loser
    else {
      zeta <- (games[[6]][game] - a) / b
      if (rbernoulli(1, p = zeta)) {
        games[[7]][game] <- 2
        games[[8]][game] <- 1
      }
      else {
        games[[7]][game] <- 1
        games[[8]][game] <- 2
      }
    }
  }
  return(games)
}
```
